FictionEro - Affective Impact of Fiction

### 2025-11-24 analysis/analysis.qmd
updated scripts

```{r}
params_table <- function(m) {
  d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
  t <- bayestestR::describe_posterior(d, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
  out <- insight::format_table(t)
  out |> 
    mutate(col = t$pd) |> 
    gt::gt() |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.95, palette = "yellow") |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.97, palette = "green") |> 
    gt::cols_hide("col")
 }
```

```{r}
# arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

@@

```{r}
params_table(arousal1)
summary(arousal1, robust = TRUE)
```

>>>>

```{r}
params_table <- function(m) {
  d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
  t <- bayestestR::describe_posterior(d, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
  out <- insight::format_table(t)
  out |> 
    mutate(col = t$pd) |> 
    gt::gt() |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.95, palette = "yellow") |> 
    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
                   row = col > 0.97, palette = "green") |> 
    gt::cols_hide("col")
}

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

<!-- - condition as random intercept for participant converged but not sure whether we should keep intercepts different or the same for the models? -->

<!-- ```{r} -->

<!-- m_arousal1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Relevance / Condition + (Relevance | Participant) + (Relevance|Item), data=df1, family=glmmTMB::ordbeta(), control = glmmTMB::glmmTMBControl(parallel = 8)) -->

<!-- m_arousal2 <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + (1| Participant) + (1|Item), family=glmmTMB::ordbeta(), data=df2, control = glmmTMB::glmmTMBControl(parallel = 8)) -->
<!-- ``` -->

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

@@

<!-- ```{r} -->
<!-- results_table(m_arousal1) -->
<!-- results_table(m_arousal2) -->
<!-- ``` -->

```{r}
params_table(m_arousal1)
summary(arousal1, robust = TRUE)
```
